Article counts per year figure

### 2022-01-27 article-counts-per-year-figure.Rmd
added ggplot2 code

---
title: "Citations figure"
author: "Fred Boehm & Xiang Zhou"
date: "1/26/2022"
output: html_document
---

@@

```{r, eval = FALSE}
remotes::install_github("akshaynagpal/RgScholar")
```

```{r}
RgScholar::google_Scholar(user_query = "mendelian randomization", year_low = 2021)
```

>>>>

---
title: "Article counts per year figure"
author: "Fred Boehm"
date: "1/26/2022"
output: html_document
---

@@

I manually recorded the article counts per year for two searches: 
1. genome-wide association study and 2. mendelian randomization.

```{r}
library(dplyr)
dat <- readxl::read_xlsx(path = "data/publication-counts.xlsx", sheet = "counts")
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = mrcount)) + ggplot2::geom_bar(stat = "identity")
```

```{r}
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = gwascount)) + ggplot2::geom_bar(stat = "identity")

```
